Traffic Aware Resource Allocation Schemes for Multi-Cell \acs{MIMO}-\acs{OFDM} Systems

### 2015-11-17 Report/convergence_centralized.tex
ccc

To ensure the uniqueness of the transmit and the receive beamformers, the objective function of the convex subproblems in \eqref{eqn-9} and \eqref{eqn-mse-2} are regularized by a strongly convex function in each \ac{SCA} iteration \eqn{k} and \ac{AO} update step \eqn{i} as 
\begin{IEEEeqnarray}{rCl} \neqsub
\hat{f}(\mbf{z}) &=& \| \tilde{\mbf{v}} \|_q \eqsub \label{orig_obj} \\ 
f(\mbf{z}) &=& \hat{f}(\mbf{z}) + {\tau}_k^{(i)} \, \| \mbf{z} - \mbf{z}^{(i)}_{k} \|^2_2 \eqsub \label{mod_obj} 
\end{IEEEeqnarray}
where \eqn{\mbf{z}} is a vector stacking all optimization variables, which can be either \eqn{[\mx,\iter{\my}{\lpoint}{i-1},\mz]} or \eqn{[\iter{\mx}{\lpoint}{i},\my,\mz]} depending on the problem and \eqn{\mbf{z}^{(i)}_{k} \triangleq [\mx_{k}^{(i)},\iter{\my}{\lpoint}{i-1},\mz_{k}^{(i)}]} is the solution obtained in the previous \eqn{\ith{(k-1)}} \ac{SCA} step. The positive constant \me{{\tau}_{k}^{(i)} > 0} ensures strong convexity of \eqn{f} in each step \cite{scutari-1}. Thus, due to strong convexity in \eqn{f}, uniqueness of the minimizer is ensured in each \ac{SCA} step \cite{yang_yang,scutari-1}.

@@

where \eqn{c > 0} be the constant of strong convexity, defined as \eqn{c \triangleq \min_{k} \{{\tau}_{k}^{(i)}\}}, and \eqn{\iter{\mbf{z}}{k+1}{i}} is the solution. Therefore, by using \eqref{strict_monotonicity} and \eqn{\iter{\mbf{z}}{k}{i} \in \iter{\mc{X}}{k}{i}}, we can show that \eqn{f(\iter{\mbf{z}}{k}{i}) > f(\iter{\mbf{z}}{k+1}{i})} holds strictly in each \ac{SCA} step unless \eqn{\mbf{z}_{k}^{(i)} \to \mbf{z}_{\lpoint}^{(i)}} as \eqn{k \to \infty}. Now, by utilizing the facts that (i) \eqn{\{f(\mbf{z}^{(i)}_k)\}} is monotonic, and (ii) the uniqueness of the minimizer (see \eqref{strict_monotonicity}), strict monotonicity of \eqn{\{f(\mbf{z}^{(i)}_k)\}} is ensured in every \ac{SCA} update \cite{scutari2010convex}. \reviewF{Since the sequence \eqn{\{f(\mbf{z}_k^{(i)})\}} is strictly decreasing and bounded, the convergence in each \ac{AO} step \eqn{{i}} is guaranteed. Let \eqn{\mbf{z}_{\lpoint}^{(i)} \triangleq \{\iter{\mx}{\lpoint}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{\lpoint|\my}{i}\}} be the solution obtained upon convergence of the objective sequence in the \eqn{\ith{i}} \ac{AO} iteration.}

@@

\subsection{Stationarity of Limit Points} \label{c-b}
\reviewF{We discuss the convergence of the iterates generated by the iterative algorithm. In order to do that, let us use consider a single global indexing \eqn{t} to represent both \ac{SCA} step \eqn{k} and \ac{AO} index \eqn{i}. It corresponds to every \ac{AO} iterations and \ac{SCA} updates performed within each of the \ac{AO} step.
Using unified index \eqn{t}, we denote iterate \eqn{\ma^{t}} as a vector staking all optimization variables produced in every \ac{SCA} iteration \eqn{{k}} and \ac{AO} step \eqn{{i}}.

>>>>

To ensure the uniqueness of the transmit and the receive beamformers, the objective function of the convex subproblems in \eqref{eqn-9} and \eqref{eqn-mse-2} are regularized by a strongly convex function in each \ac{SCA} iteration \eqn{k} and \ac{AO} update step \eqn{i} as 
\begin{IEEEeqnarray}{rCl} \neqsub
\hat{f}(\mbf{z}) &=& \| \tilde{\mbf{v}} \|_q \eqsub \label{orig_obj} \\ 
f(\mbf{z}) &=& \hat{f}(\mbf{z}) + {\tau}_k^{(i)} \, \| \mbf{z} - \mbf{z}^{(i)}_{k} \|^2_2 \eqsub \label{mod_obj} 
\end{IEEEeqnarray}
where \eqn{\mbf{z}} is a vector stacking all optimization variables, which can be either \eqn{[\mx,\iter{\my}{\lpoint}{i-1},\mz]} or \eqn{[\iter{\mx}{\lpoint}{i},\my,\mz]} depending on the problem and \eqn{\mbf{z}^{(i)}_{k} \triangleq [\mx_{k}^{(i)},\iter{\my}{\lpoint}{i-1},\mz_{k}^{(i)}]} is the solution obtained in the previous \eqn{\ith{(k-1)}} \ac{SCA} step. The positive constant \me{{\tau}_{k}^{(i)} > 0} ensures strong convexity of \eqn{f} in each step \cite[Sec. 3.4.3]{bertsekas1989parallel}. Thus, due to strong convexity in \eqn{f}, uniqueness of the minimizer is ensured in each \ac{SCA} step \cite{yang_yang,scutari-1}.

@@

where \eqn{c > 0} be the constant of strong convexity, defined as \eqn{c \triangleq \min_{k} \{{\tau}_{k}^{(i)}\}}, and \eqn{\iter{\mbf{z}}{k+1}{i}} is the solution. Therefore, by using \eqref{strict_monotonicity} and \eqn{\iter{\mbf{z}}{k}{i} \in \iter{\mc{X}}{k}{i}}, we can show that \eqn{f(\iter{\mbf{z}}{k}{i}) > f(\iter{\mbf{z}}{k+1}{i})} holds strictly in each \ac{SCA} step unless \eqn{\mbf{z}_{k}^{(i)} \to \mbf{z}_{\lpoint}^{(i)}} as \eqn{k \to \infty}. Now, by utilizing the facts that (i) \eqn{\{f(\mbf{z}^{(i)}_k)\}} is monotonic, and (ii) the uniqueness of the minimizer (see \eqref{strict_monotonicity}), strict monotonicity of \eqn{\{f(\mbf{z}^{(i)}_k)\}} is ensured in every \ac{SCA} update \cite{scutari2010convex}. \reviewF{Since the objective is strictly decreasing and bounded, convergence of \eqn{\{f(\mbf{z}_k^{(i)})\}} is guaranteed in every \ac{AO} step \eqn{i}. Let \eqn{\mbf{z}_{\lpoint}^{(i)} \triangleq \{\iter{\mx}{\lpoint}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{\lpoint|\my}{i}\}} be the solution obtained upon convergence of the objective sequence in the \eqn{\ith{i}} \ac{AO} update.}

@@

\subsection{Stationarity of Limit Points} \label{c-b}
\reviewF{We discuss the convergence of the iterates generated by the iterative algorithm. In order to do that, let us use consider a single global indexing \eqn{t} to represent both \ac{SCA} step \eqn{k} and \ac{AO} index \eqn{i}. It corresponds to every \ac{AO} iterations and \ac{SCA} updates performed within each of the \ac{AO} step.
Using the unified index \eqn{t}, we denote iterate \eqn{\ma^{t}} as a vector staking all optimization variables produced in every \ac{SCA} iteration \eqn{{k}} and \ac{AO} step \eqn{{i}}.

### 2015-11-17 Report/convergence_distributed.tex
ccc

The convergence of the distributed algorithm in Algorithm \ref{algo-3} follows the same discussion as the one in Appendix \ref{sec-3.5}, if the subproblem in \eqref{eqn-decent-1} converges to the centralized solution. Note that \eqref{eqn-decent-1} satisfies the Slater's constraint qualification by having a non-empty interior and a compact set, which are required for the convergence. Since in primal decomposition, the master subproblem uses subgradient to update the coupling interference vectors in consensus with the objective function, the convergence of the subproblem is guaranteed as \me{i \to \infty} for a diminishing step size as shown in \cite{scutari_1},\cite[Prop 8.2.6]{bertsekas2003convex}.

To show the convergence of the \ac{ADMM}, we use the discussion in \cite[Prop. 4.2]{bertsekas1989parallel} and \cite{boyd2011distributed} by writing \eqref{eqn-dual-3} as
\begin{IEEEeqnarray}{rCl} \neqsub
	\underset{\mbf{x} \in \mc{C}_1,\mbf{z} \in \mc{C}_2}{\text{minimize}} &\quad& G(\mbf{x}) + H(\mbf{z}) \eqsub \\
	\text{subject to} &\quad& \mbf{A} \mbf{x} = \mbf{z} \eqsub \label{const-admm}
\end{IEEEeqnarray}
where the constraint in \eqref{const-admm} is identical to that in \eqref{const-admm1} used in the \ac{ADMM} subproblem \eqref{eqn-dual-3}. 
To show the convergence, we rely on the following conditions. (i) \me{G,H} should be convex. (ii) \me{\mc{C}_1,\mc{C}_2} should be a convex set and bounded. (iii) \me{\mbf{A}^\herm \mbf{A}} should be invertible. It is evident from the equality constraints \eqref{const-admm} and \eqref{const-admm1} that \me{\mbf{A} = \mbf{I}}, and therefore it is invertible. Note that the objective functions \me{G,H} include \me{\ell_q} norm and an additional quadratic term as in \eqref{mod_obj}, thereby exhibiting strong convexity. Moreover, the feasible set defined by the constraints of \eqref{eqn-decent-1} is convex and has a nonempty interior. Now, by using \cite[Prop. 4.2]{bertsekas1989parallel}, we can show that the \ac{ADMM} converges to the centralized solution as \me{i \to \infty} by using diminishing step size in each \ac{ADMM} iteration as discussed in \cite{boyd2011distributed}. Therefore, if both the primal and \ac{ADMM} approaches are allowed to converge to the centralized solution in each \ac{SCA} step, \reviewF{then every limit point of the sequence generated by the distributed schemes is a stationary point of \eqref{con}, by following the discussions presented in Appendix \ref{sec-3.5}.}

@@

Unlike the primal or the \ac{ADMM} methods, the decomposition approach via \ac{KKT} conditions, presented in Section \ref{sec-4.3}, updates all the optimization variables at once, \textit{i.e}, the \ac{SCA} update of \me{\epsilon^{(i-1)}}, the \ac{AO} update of \me{\mvec{w}{l,k,n}} and the dual variable update of \me{\alpha} using subgradient method. Therefore, it is difficult to theoretically prove the convergence of the algorithm to a stationary point of the nonconvex problem in \eqref{eqn-6}.

@@

However, to avoid the nested iterations, the proposed method performs block update of all variables at once to obtain transmit and receive beamformers for limited number of iterations, thus, achieving improved speed of convergence. Since the optimization variables are updated together, it is theoretically difficult to prove the monotonicity of the objective in each block update. Therefore, the convergence of the sequence of iterates generated by the Algorithm \ref{algo-4} is not guaranteed. Moreover, the objective function used to obtain the iterative algorithm is not strongly convex, and therefore the uniqueness of the iterates is also not guaranteed in each update. Thus, the iterative scheme outlined in Algorithm \ref{algo-4} cannot be guaranteed to find a fixed point to ensure the convergence of the sequence of beamformer iterates.

>>>>

\reviewF{Assuming a regularized objective function as in \eqref{mod_obj} for each subproblem \eqref{eqn-decent-1}, convergence of Algorithm \ref{algo-3} follows the discussions in Appendix \ref{sec-3.5}, if in each \ac{SCA} step, the primal decomposition converges to the centralized solution. It can be ensured by the following properties. (i) The feasible set has a non-empty interior and bounded, therefore, each subproblem satisfies the Slater's constraint qualifications. (ii) Due to the strongly convex objective \eqref{mod_obj} in each subproblem, uniqueness of the minimizer is guaranteed. Therefore, by using the above facts, convergence of the primal decomposition algorithm can be ensured as \eqn{j \to \infty} using \cite[Prop. 8.2.6]{bertsekas2003convex} by considering diminishing step size in each subgradient update.}

Now, to show the convergence of \ac{ADMM}, we use the discussion in \cite[Prop. 4.2]{bertsekas1989parallel} and \cite{boyd2011distributed} by writing \eqref{eqn-dual-3} as
\begin{IEEEeqnarray}{rCl} \neqsub
	\underset{\mbf{x} \in \mc{C}_1,\mbf{z} \in \mc{C}_2}{\text{minimize}} &\quad& G(\mbf{x}) + H(\mbf{z}) \eqsub \\
	\text{subject to} &\quad& \mbf{A} \mbf{x} = \mbf{z} \eqsub \label{const-admm}
\end{IEEEeqnarray}
where the constraint in \eqref{const-admm} is identical to that of \eqref{const-admm1} used in the \ac{ADMM} subproblem \eqref{eqn-dual-3}. 
To show the convergence, we rely on the following conditions. (i) \me{G,H} should be convex. (ii) \me{\mc{C}_1,\mc{C}_2} should be a convex set and bounded. (iii) \me{\mbf{A}^\herm \mbf{A}} should be invertible. It is evident from the equality constraints \eqref{const-admm} and \eqref{const-admm1} that \me{\mbf{A} = \mbf{I}}, and therefore it is invertible. Note that the objective functions \me{G,H} include \me{\ell_q} norm and an additional quadratic term as in \eqref{mod_obj}, thereby exhibiting strong convexity. Moreover, the feasible set defined by the constraints of \eqref{eqn-decent-1} is convex and has a nonempty interior. Now, by using \cite[Prop. 4.2]{bertsekas1989parallel}, we can show that the \ac{ADMM} algorithm converges to the centralized solution as \me{j \to \infty} by using diminishing step size in each \ac{ADMM} update as discussed in \cite{boyd2011distributed}. Therefore, if both the primal and \ac{ADMM} approaches are allowed to converge to the centralized solution in each \ac{SCA} step, \reviewF{then every limit point of the sequence generated by the distributed schemes is a stationary point of \eqref{con}, by following the discussions in Appendix \ref{sec-3.5}.}

@@

Unlike the primal or the \ac{ADMM} approaches, the decomposition method via \ac{KKT} conditions, presented in Section \ref{sec-4.3}, updates all the optimization variables at once, \textit{i.e}, the \ac{SCA} update of \me{\epsilon^{(i-1)}}, the \ac{AO} update of \me{\mvec{w}{l,k,n}} and the dual variable update of \me{\alpha} using subgradient method. Therefore, it is difficult to theoretically prove the convergence of the algorithm to a stationary point of the nonconvex problem in \eqref{eqn-6}.

@@

However, to avoid the nested iterations, the proposed method performs block update of all variables at once to obtain transmit and receive beamformers for limited number of iterations, thus, achieving improved speed of convergence. Since the optimization variables are updated together, it is theoretically difficult to prove the monotonicity of the objective in each block update. Therefore, the convergence of the sequence of iterates generated by the Algorithm \ref{algo-4} is not guaranteed. Moreover, the objective function used to obtain the iterative algorithm is not strongly convex, and therefore the uniqueness of the iterates is also not guaranteed in each update. Thus, the iterative scheme outlined in Algorithm \ref{algo-4} cannot be guaranteed to find a fixed point to ensure convergence.

### 2015-11-17 Report/dual_approach.tex
ccc

The convergence analysis for the distributed algorithms is provided in Appendix \ref{sec-dist-conv}. To reduce the amount of information exchange among the coupling \acp{BS}, often distributed schemes are iterated for few steps, say, \eqn{J_{\max}}. If so, the convergence of the iterates is not guaranteed, since it is difficult to show the monotonicity of objective in each \ac{SCA} step. The reason is that in each primal or \ac{ADMM} update, the global objective need not be decreasing monotonically, despite reaching the centralized solution upon convergence. However, if the following conditions are satisfied in each \ac{SCA} step, \textit{i.e.}, (i) by ensuring uniqueness of the minimizer, and (ii) by choosing \eqn{J_{\max}} to be sufficiently large in order to ensure strict monotonicity of the objective, \reviewF{then the convergence discussions follows Appendices \ref{sec-3.5} and \ref{sec-dist-conv}}. Moreover, if the receivers are updated together with the transmit precoders as in Algorithm \ref{algo-3}, then strict monotonic decrease of the objective sequence is still ensured. The reason is that the \ac{MMSE} receiver is optimal for the fixed transmit precoders obtained after each \ac{SCA} update.

>>>>

Assuming that the following conditions are satisfied in each \ac{SCA} step, \textit{i.e.}, (i) by ensuring uniqueness of the minimizer, and (ii) by choosing \eqn{J_{\max}} to be sufficiently large in order to ensure strict monotonicity of the objective, \reviewF{then the convergence follows the discussions in Appendices \ref{sec-3.5} and \ref{sec-dist-conv}}. Moreover, if the receivers are updated together with the transmit precoders as in Algorithm \ref{algo-3}, then strict monotonic decrease of the objective sequence is still ensured. The reason is that the \ac{MMSE} receiver is optimal for the fixed transmit precoders obtained after each \ac{SCA} update. However, to reduce the amount of information exchange among the coupling \acp{BS}, often distributed schemes are iterated for few steps, say, \eqn{J_{\max}}. If so, convergence of the iterates is not guaranteed, since it is difficult to show the monotonicity of objective in each \ac{SCA} step. The reason is that in each primal or \ac{ADMM} update, the global objective need not be decreasing monotonically.

### 2015-11-17 Report/mse_formulation.tex
ccc

In all our simulations, the objective sequence generated by the Algorithm \ref{algo-1} converges. \reviewF{However, for a formal convergence analysis, we consider a regularized objective in \eqref{mod_obj} for \eqref{eqn-6.1} and \eqref{eqn-mse-1.1}. The proximal term in \eqref{mod_obj} ensures strong convexity, thereby enforcing the uniqueness of minimizer in each step. Note that the feasible set of problems \eqref{eqn-3} and \eqref{eqn-mse-1} are bounded. However, the feasible set of \eqref{eqn-6} need not be bounded due to the introduced variables in \eqref{eqn-6.2} and \eqref{eqn-6.3} to relax \eqref{eq:SINR}, since \eqn{\beta_{l,k,n}} can assume any value satisfying \eqref{eqn-6.3} without violating any other constraints in \eqref{eqn-6} when \eqn{\gamma_{l,k,n} = 0}. Therefore, by restricting \eqn{\beta_{l,k,n}}'s with a maximum interference constraint depending on \eqn{P_{\max}}, the feasible set can be bounded without altering the solution space of other variables. However, as a consequence of considering the regularized objective in \eqref{mod_obj}, the additional constraint is not required, since \eqn{\beta_{l,k,n}} is bounded due to the proximal term in \eqref{mod_obj}. With the above assumptions, convergence proof is presented in Appendix \ref{sec-3.5}.}

>>>>

In all our simulations, the objective sequence generated by the Algorithm \ref{algo-1} converges. \reviewF{However, for a formal convergence analysis, we consider a regularized objective in \eqref{mod_obj} for \eqref{eqn-6.1} and \eqref{eqn-mse-1.1}. The proximal term in \eqref{mod_obj} ensures strong convexity, thereby enforcing the uniqueness of minimizer in each step. Note that the feasible set of problems \eqref{eqn-3} and \eqref{eqn-mse-1} is bounded. However, for \eqref{eqn-6}, the feasible set need not be bounded due to newly introduced variables in \eqref{eqn-6.2} and \eqref{eqn-6.3} to relax \eqref{eq:SINR}, since \eqn{\beta_{l,k,n}} can assume any value satisfying \eqref{eqn-6.3} without violating any other constraints in \eqref{eqn-6} when \eqn{\gamma_{l,k,n} = 0}. Therefore, by restricting \eqn{\beta_{l,k,n}}'s with a maximum interference constraint depending on \eqn{P_{\max}}, the feasible set can be bounded without altering the solution space of other variables. However, as a consequence of considering the regularized objective in \eqref{mod_obj}, the additional constraint is not required, since \eqn{\beta_{l,k,n}} is bounded due to the proximal term in \eqref{mod_obj}. With the above assumptions, convergence proof is presented in Appendix \ref{sec-3.5}.}
